Physics-informed machine learning for reduced-order modelling

### 2020-06-28 manuscript/elsarticle/manuscript.tex
pc
PC-cwq

%% main text
\section{Introduction}
In recent years, although high-fidelity numerical method has witnessed substantial developments for modeling complex phenomena, it is still challenging for many applications, such as design, optimization, control and uncertainty quantification problems. Such applications are governed by parameterized partial differential equations(PDEs) \cite{hesthaven2016certified, quarteroni2015reduced}, where parameters characterize underlying geometry, boundary conditions, source terms and physical properties, etc. High-fidelity numerical method are prohibitively expensive to such applications in multi-entry and real-time contexts, due to the required lots of degrees of freedom(DOFs).
%Although increasing computational power and parallel techniques are nowadays available to largely reduce the consumed wall time, the total cost with respect to both consumed CPU time and money remains prohibitively expensive.
The need to largely reduce computational cost gives birth to reduced-order methods \cite{lucia2004reduced}, aiming at replacing the full-order system with a cheap reduced-order system with an affordable loss of accuracy.

Reduced basis (RB) method is one of the well-known and widely-used reduced-order methods, and always follows the offline-online paradigm \cite{maday2006reduced}. The offline stage comprises preparing the high-fidelity solutions(snapshots), extracting the reduced basis and building the cheap evaluation model. The reduced space, spanned by the reduced basis  extracted from the snapshots, is expected to represent the main dynamics of the full-order model. There exist many methods to extract the reduced basis, such as the Proper Orthogonal Decomposition (POD) \cite{hesthaven2016certified,liang2002proper,quarteroni2015reduced}, the  Proper Generalized Decomposition \cite{chinesta2011short}, the Piecewise Tangential Interpolation \cite{gallivan2002model}, the Matrix Interpolation \cite{panzer2010parametric}, greedy algorithms\cite{billaud2017dynamical, lappano2016greedy, hesthaven2014efficient}. Among them, the POD perhaps is the most widely-known and widely-used one, where the reduced basis is generated by a singular value decomposition (SVD) algorithm for some given snapshots with respect to a chosen set of parameters. After the reduced basis has been properly set up, an approximation to high-fidelity solution is recovered from projection coefficients of the reduced space. Then a suitable model will be built offline, aiming to provide online evaluation for a new given parameter.
For building such a model, both 'white-box' and 'black-box' strategies are applied in the literature.

Galerkin method \cite{rowley2004model, wang2020recurrent, deane1991low} is one of widely-used white-box strategies. In the offline stage,
a reduced-order model determining projection coefficients is derived from Galerkin projection of the full-order model. In the online stage, the reduced-order model is solved by a suitable numerical solver for each parameter.
As projection coefficients are directly solved by a deterministic method, the achieved approximation accuracy is always very good. what's more, no more extra snapshots is required besides the snapshots for building RB.
However, the online solving of the reduced-order model is not trivial, which remains an open problem with respect to its accuracy, stability and convergence \cite{huang2018challenges, iollo2000stability, rowley2004model}. Besides, the online solving of the reduced-order model is still time consuming especially for complex nonlinear problems, even if it is much cheaper than the solving of full-order model.

@@

The white-box Galerkin method targets the full-order model, while the black-box machine learning models target high-fidelity solutions. These two strategies approximate the parameterized PDEs in different directions.
In this work,  we try to develop a physics-informed machine learning framework using a grey-box strategy to take the advantages of the above two strategies.
Inspired by the well-know physics-informed neural network (PINN) \cite{raissi2019physics, raissi2020hidden, mao2020physics}, we can directly solve the reduced-order model by  optimizing a neural network.
Thus, we keep on the intrusive approach and utilize the reduced-order information to build a neural network.
For the PINN approach, there is no need for labeled data, thus no need for extra snapshots, and what we need to do is to train a network to satisfy the reduced-order model in some sense.
Besides this approach,  the projection coefficients of snapshots can also be added into the training of network, although they are not the solutions of the reduced-order model. we term this approach as the physics-reinforced neural network (PRNN).
For both PINN and PRNN approaches, they enjoy a higher accuracy and independence of extra snapshots inherited from Galerkin method, and also the effectiveness inherited from machine learning models.
To test assertion, the PINN and PRNN are applied to one-dimensional Burges' equation, two-dimensional lid-driven flow and natural convection in enclosure. A detailed comparison with the white-box POD-G method and the black-box POD-NN method proposed by Jan et al.\cite{hesthaven2018non} is analysed for the three test cases.

The remainder of this paper is organized as follows. Section 2 presents the framework from parameterized PDEs to the reduced-order model. Section 3 briefly introduce the POD-NN method (referred to PDNN in this work) and presents the derivation of PINN and PRNN method based on the reduced-order information. Section 4 details some numerical setups for these methods, and offers some numerical results to show the superiority of the proposed methods, In Section 5, some conclusions are given.

\section{Projection-based reduced basis method}\label{sec:POD-G}
Consider a nonlinear dynamic system governed by the following parameterized partial differential equations(PDEs):
\begin{equation}
\begin{aligned}
\mathcal{N}\left(\phi\left(\mathbf{x}\right); \pmb{\mu}\right)=0&,  \qquad \mathbf{x} \in \Omega\left(\pmb{\mu}\right)  \\
\mathcal{B}\left(\phi\left(\mathbf{x}\right); \pmb{\mu}\right)=0&,  \qquad \mathbf{x} \in \partial \Omega\left(\pmb{\mu}\right)
\end{aligned}
\label{eq_GoverningEqs}
\end{equation}
where $\mathcal{N}$ is a general nonlinear differential operator, $\phi\left(\mathbf{x}\right)$ are field variables to be solved on Cartesian coordinates $\mathbf{x}$. $\mathcal{B}$ are operators defining boundary conditions for the boundary $\partial \Omega$ of the physical  domain $\Omega$. $\pmb{\mu} \in \mathcal{P}$ are specific parameters characterizing the nonlinear dynamic system as well as the physical domain $\Omega$, where $\mathcal{P}$ is the parameter space.

As is always the case for reduced-order methods, a dynamic system is approximated by finding the its projection in a space spanned by a few well-chosen basis vectors. These basis are generated from a suitable linear combination of some precomputed high-fidelity approximations, termed as snapshots. To ensure the compatibility among snapshots, the variable physical domain has to be addressed. To this end, the variable physical domain will be mapped into a fixed computational domain with the same collation of degrees of freedom. This can be implemented by an invertible problem-dependent mapping $\mathcal{X} : \mathbf{x} \in \Omega\left(\pmb{\mu}\right) \to \pmb{ \xi} \in \widetilde \Omega$, which reads
\begin{equation}
\pmb{ \xi} = \mathcal{X} \left( \mathbf{x}; \pmb{\mu} \right),
\label{eq_Transform}
\end{equation}
and thus the governing equations (\ref{eq_GoverningEqs}) are recast as follows:
\begin{equation}
\begin{aligned}
\mathcal{N}\left(\phi\left( \mathcal{X}^{-1} \left( \pmb{ \xi}; \pmb{\mu} \right) \right); \pmb{\mu}\right)
&:=\widetilde {\mathcal{N}} \left(\phi\left( \pmb{ \xi} \right); \pmb{\mu}\right)
=0,  \qquad \pmb{ \xi} \in \widetilde \Omega
\\
\mathcal{B}\left(\phi\left(\mathcal{X}^{-1} \left( \pmb{ \xi}; \pmb{\mu} \right)\right); \pmb{\mu}\right)
&:=\widetilde {\mathcal{B}} \left(\phi\left( \pmb{ \xi} \right); \pmb{\mu}\right)
=0,  \qquad \pmb{ \xi} \in \partial \widetilde \Omega
\end{aligned}
\label{eq_GoverningEqsForXi}
\end{equation}
where $\widetilde \Omega$ is the computational domain, $\widetilde {\mathcal{B}}$ and $\widetilde {\mathcal{N}}$ are the derived operators in computational space resulting from the transformation Eq. (\ref{eq_Transform}).

@@

Here we denote the discrete solutions of Eq ( \ref{eq_GoverningEqsForXi}) in vector form $\pmb{\phi} _h \in \mathbf{R}^{N  }$ and $\pmb{\phi} _h^{B} \in \mathbf{R}^{N_B}$ for parameter $\pmb{\mu}  \in \mathcal{P}$.
Given a suitable HF method, we have the governing Eq. (\ref{eq_GoverningEqsForXi}) in discrete form
\begin{align}
\mathbf{L}_{\widetilde {\mathcal{N}}}\pmb{\phi}_h +g_{\widetilde {\mathcal{N}}}(\pmb{\phi}_h, \pmb{\phi}_h^{B})
+\mathbf{C}_{\widetilde {\mathcal{N}}}
= 0
\label{eq_DiscreteEqs}
\\
\mathbf{L}_{\widetilde {\mathcal{B}}} \pmb{\phi}_h + \mathbf{L}_{\widetilde {\mathcal{B}}}^{B} \pmb{\phi}_h^{B}
+\mathbf{C}_{\widetilde {\mathcal{B}}}
= 0
\label{eq_DiscreteBoundary}
\end{align}
where $\mathbf{L}_{\widetilde {\mathcal{N}}} \in \mathbf{R}^{N \times N}$, $\mathbf{L}_{\widetilde {\mathcal{B}}} \in \mathbf{R}^{N_B \times N}$ and $\mathbf{L}_{\widetilde {\mathcal{B}}}^{B} \in \mathbf{R}^{N_B \times N_B}$ represent matrixes derived from linear parts of operators $\widetilde {\mathcal{N}}$ and $\widetilde {\mathcal{B}}$.
$\mathbf{C}_{\widetilde {\mathcal{N}}} \in \mathbf{R}^{N}$ and $\mathbf{C}_{\widetilde {\mathcal{B}}} \in \mathbf{R}^{N_B}$ are constant vectors independent of $\pmb{\phi} _h$ and $\pmb{\phi} _h^B$.
$g_{\widetilde {\mathcal{N}}}: \mathbf{R}^N \times \mathbf{R}^{N_B} \mapsto \mathbf{R}^N$ is a nonlinear function derived from the nonlinear part of operator $\widetilde {\mathcal{N}}$.

@@

\subsubsection{Chebyshev pseudospectral method}
In the Chebyshev pseudospectral method, the $d$-dimensional variable physical domain of  will be mapped into a unit regular computational domain $\widetilde \Omega =[-1,1]^d$,  each dimension discretized by  $N_p+1$ Chebyshev-Gauss-Lobatto points,
\begin{equation}
\xi_i=\cos \left( \frac{\pi i}{N_p} \right), \quad 0 \le i \le {N_p}
\label{eq_CollocationPoints}
\end{equation}
Spatial derivatives in operators $\widetilde {\mathcal{N}}$ and $\widetilde {\mathcal{B}}$ are approximated with a matrix-vector multiplication in each dimension. In each dimension, the derivatives are approximated as follows:
\begin{equation}
\left. { \frac{\partial^s    \phi}{{\partial \xi^s}  }} \right|_{\xi _i }
 = \mathbf{D}^s \pmb{\phi}
\end{equation}
where $\pmb{\phi}=\{\phi _i\}_{i=0}^{N_p}$, $s$ is the order of derivative and $\mathbf{D}^s$ is the $s$th-order difference matrix of size ${(N_p+1)\times (N_p+1)}$ with entries defined by
\begin{equation}
D^0_{i,j} = \delta_{ij} \qquad 0 \le i,j \le {N_p},
\label{eq_D0}
\end{equation}
\begin{equation}
\left\{ \begin{aligned}
&D_{i,j}^1 = \frac{{{B_i}}}{{{B_j}}}\frac{{{{( - 1)}^{i + n}}}}{{2\sin \left( {\frac{{(i + j)\pi }}{{2{N_x}}}} \right)\sin \left( {\frac{{(j - i)\pi }}{{2{N_p}}}} \right)}} \qquad 0 \le i,j \le {N_p},i \ne j\\
&D_{i,i}^1 =  - \sum\limits_{j = 0,j \ne i}^{{N_p}} {D_{i,j}^1} \quad 1 \le i \le {N_p} - 1\\
&D_{0,0}^1 =  - D_{{N_p},{N_p}}^1 =  - \frac{{2{N_p}^2 + 1}}{6}{\rm{                       }}\\
&{B_i} = \left\{
                 \begin{array}{*{20}{l}}
                      2 \qquad i=0, N_p \\
                      1 \qquad 1 \le i \le {N_p-1}
                 \end{array}
                 \right.
\end{aligned} \right. ,
\label{eq_D1}
\end{equation}
\begin{equation}
D^s_{i,j} = D^{1}_{i,k}D^{s-1}_{k,j} \qquad 0 \le i,j,k \le {N_p}.
\label{eq_Ds}
\end{equation}

For the following simulations of flow problems, the well known $IP_N-IP_{N-2}$ method \cite{zhang2010explicit} is adopted to prevent spurious pressure mode from
contaminating the flow fields \cite{peyret2013spectral}. In the $IP_N-IP_{N-2}$ method, pressure derivative is approximated without pressure values at boundary points, and thus pressure is approximated with polynomial of two order lower than all other field variables, such as velocity and temperature. All other variables are discretized with Eqs. (\ref{eq_D0})-(\ref{eq_Ds}) except that the first-order difference matrix $\mathbf{D}^{1}$ of pressure is replaced with $\hat {\mathbf{D}}^1$ as follows
\begin{equation}
\left\{ \begin{aligned}
&\hat D_{i,j}^1 = 0                              & i=0,N_p \text{  or } j=0, N_p \\
&\hat D_{i,i}^1 = \frac{3\xi_i}{2(1-\xi_i^{2})}  & 1 \le i \le N_p-1\\
&\hat D_{i,j}^1 = \frac{(-1)^{i+j}(1-\xi_j^{2})}
{2(1-\xi_i^{2})(\xi_i-\xi_j)} \qquad             & 1 \le i \ne j \le N_p-1\\
\end{aligned} \right. ,
\label{eq_D1}
\end{equation}

@@

\subsection{Reduced-order model}
\label{sec_ROM}
As for solving the problem in Eq. (\ref{eq_GoverningEqsForXi}), full-order model is always suffering from large computational cost since the required degrees of freedom $N$ is always very large.  Therefore, we are interested in replacing the full-order model with a well-posed  reduced-order model to represent main dynamic of the system. The full-order model is termed as reducible when high-fidelity solution $\pmb{\phi} _h$ can be well approximated in $m$-dimensional subspace $\mathcal{V}=\mathbf{R}^{N \times m}$. The subspace is spanned by a suitable set of basis vectors $\{\mathbf{V}_i \in \mathbf{R}^{N} \}_{i=1}^m$.  Note that the the size of problem will be largely reduced, only if $m \ll N$. The full-order solution of the interior DOFs $\pmb{\phi} _h$ can be projected into the subspace $\mathcal{V}$ by
\begin{equation}
\begin{aligned}
\pmb{\phi} _h  &   =   \mathbf{V} \pmb{\alpha} + \tilde{\phi} + \pmb{\epsilon}
               &\approx \mathbf{V} \pmb{\alpha} + \tilde{\phi},
\end{aligned}
\label{eq_projection}
\end{equation}
where $\mathbf{V} \in \mathbf{R}^{N\times m}$ is a matrix with the basis vectors as its columns, $\pmb{\alpha}$ is   the projection coefficients, $\pmb{\epsilon}$ is the projection error. $\tilde{\phi} \in \mathbf{R}$ is independent of $\pmb{\mu}$, intended for filtering a constant value to avoid its domination on the basis, and usually it can be set as the average. The boundary conditions in Eq. (\ref{eq_DiscreteBoundary}) say that the interior DOFs have a linear relationship with interior DOFs. Thus, we can enforce the boundary conditions without any reduction. The procedure keeps the reduced-order model of high accuracy at bounaries and avoid shifting of boundary values. According to Eq.(\ref{eq_DiscreteBoundary}), the boundary DOFs can be denoted as follows
\begin{equation}
\pmb{\phi}_h^{B} = -( \mathbf{L}_{\widetilde {\mathcal{B}}}^{B} )^{-1}
\left(
\mathbf{L}_{\widetilde {\mathcal{B}}} \pmb{\phi}_h +
\mathbf{C}_{\widetilde {\mathcal{B}}}
\right)
\label{eq_DerivePhiB}
\end{equation}

>>>>

%% main text
\section{Introduction}
In recent years, although high-fidelity numerical method has witnessed substantial developments for modeling complex phenomena, it is still challenging for many applications, such as design, optimization, control and uncertainty quantification problems. Such applications are governed by parameterized partial differential equations(PDEs) \cite{hesthaven2016certified, quarteroni2015reduced}, where parameters characterize underlying geometry, boundary conditions, source terms and physical properties, etc. High-fidelity numerical method are prohibitively expensive to such applications in multi-entry and real-time contexts, due to the required lots of degrees of freedom(DOFs).
%Although increasing computational power and parallel techniques are nowadays available to largely reduce the consumed wall time, the total cost with respect to both consumed CPU time and money remains prohibitively expensive.
The need to largely reduce computational cost gives birth to reduced-order modeling methods \cite{lucia2004reduced}, aiming at replacing the full-order system with a cheap reduced-order system with an affordable loss of accuracy.

Reduced basis (RB) method is one of the well-known and widely-used reduced-order modeling methods, and always follows the offline-online paradigm \cite{maday2006reduced}. The offline stage comprises preparing high-fidelity solutions(snapshots), extracting the reduced basis and building a cheap evaluation model. The reduced space, spanned by the reduced basis  extracted from the snapshots, is expected to represent the main dynamics of the full-order model. There exist many methods to extract the reduced basis, such as the Proper Orthogonal Decomposition (POD) \cite{hesthaven2016certified,liang2002proper,quarteroni2015reduced}, the  Proper Generalized Decomposition \cite{chinesta2011short}, the Piecewise Tangential Interpolation \cite{gallivan2002model}, the Matrix Interpolation \cite{panzer2010parametric}, greedy algorithms\cite{billaud2017dynamical, lappano2016greedy, hesthaven2014efficient}. Among them, the POD perhaps is the most widely-known and widely-used one, where the reduced basis is generated by a singular value decomposition (SVD) algorithm for some given snapshots with respect to a chosen set of parameters. After the reduced basis has been properly set up, an approximation to high-fidelity solution is recovered from projection coefficients of the reduced space. Then a suitable model will be built offline, aiming to provide online evaluation for a new given parameter.
For building such a model, both 'white-box' and 'black-box' strategies are applied in the literature.

Galerkin method \cite{rowley2004model, wang2020recurrent, deane1991low} is one of widely-used white-box strategies. In the offline stage,
a reduced-order model determining projection coefficients is derived from Galerkin projection of the full-order model. In the online stage, the reduced-order model is solved by a suitable numerical solver for each parameter.
As projection coefficients are directly solved by a deterministic method, the achieved approximation accuracy is always very good. What's more, no more extra snapshots is required besides the snapshots for building RB.
However, the online solving of the reduced-order model is not trivial, which remains an open problem with respect to its accuracy, stability and convergence \cite{huang2018challenges, iollo2000stability, rowley2004model}. Besides, the online solving of the reduced-order model is still time consuming especially for complex nonlinear problems, even if it is much cheaper than the solving of full-order model.

@@

The white-box Galerkin method targets the full-order model, while the black-box machine learning models target high-fidelity solutions. These two strategies approximate the parameterized PDEs in different directions.
In this work,  we try to develop a physics-informed machine learning framework using a grey-box strategy to take the advantages of the above two strategies.
Inspired by the well-know physics-informed neural network (PINN) \cite{raissi2019physics, raissi2020hidden, mao2020physics}, we can directly solve the reduced-order model by  optimizing a neural network.
Thus, we keep on the intrusive approach and utilize the reduced-order information to build a neural network.
For the PINN approach, there is no need for labeled data, thus no need for extra snapshots, and what we need to do is to train a network to satisfy the reduced-order model in some sense.
Besides this approach,  the projection coefficients of snapshots can also be added into the training of network, although they are not the solutions of the reduced-order model. we term this approach as the physics-reinforced neural network (PRNN).
For both PINN and PRNN approaches, they enjoy a higher accuracy and independence of extra snapshots inherited from Galerkin method, and also the effectiveness inherited from machine learning models.
To test this assertion, the PINN and PRNN are applied to one-dimensional Burges' equation, two-dimensional lid-driven flow and natural convection in enclosure. A detailed comparison with the white-box POD-G method and the black-box POD-NN method proposed by Jan et al.\cite{hesthaven2018non} is analysed for the three test cases.

The remainder of this paper is organized as follows. Section 2 presents the framework from parameterized PDEs to the reduced-order model. Section 3 briefly introduce the POD-NN method (referred to PDNN in this work) and presents the derivation of PINN and PRNN method based on the reduced-order information. Section 4 details some numerical setups for these methods, and offers some numerical results to show the superiority of the proposed PINN and PRNN methods, In Section 5, some conclusions are given.

\section{Projection-based reduced basis method}\label{sec:POD-G}
Consider a nonlinear dynamic system governed by the following parameterized partial differential equations(PDEs):
\begin{equation}
\begin{aligned}
\mathcal{N}\left(\phi\left(\mathbf{x}\right); \pmb{\mu}\right)=0&,  \qquad \mathbf{x} \in \Omega\left(\pmb{\mu}\right),  \\
\mathcal{B}\left(\phi\left(\mathbf{x}\right); \pmb{\mu}\right)=0&,  \qquad \mathbf{x} \in \partial \Omega\left(\pmb{\mu}\right),
\end{aligned}
\label{eq_GoverningEqs}
\end{equation}
where $\mathcal{N}$ is a general nonlinear differential operator, $\phi\left(\mathbf{x}\right)$ are field variables to be solved on Cartesian coordinates $\mathbf{x}$. $\mathcal{B}$ are operators defining boundary conditions for the boundary $\partial \Omega$ of the physical  domain $\Omega$. $\pmb{\mu} \in \mathcal{P}$ are specific parameters characterizing the nonlinear dynamic system as well as the physical domain $\Omega$, where $\mathcal{P}$ is the parameter space.

As is always the case for reduced-order methods, a dynamic system is approximated by finding the its projection in a space spanned by a few well-chosen basis vectors. These basis are generated from a suitable linear combination of some precomputed high-fidelity approximations, termed as snapshots. To ensure the compatibility among snapshots, the variable physical domain has to be addressed. To this end, the variable physical domain will be mapped into a fixed computational domain with the same collation of degrees of freedom. This can be implemented by an invertible problem-dependent mapping $\mathcal{X} : \mathbf{x} \in \Omega\left(\pmb{\mu}\right) \to \pmb{ \xi} \in \widetilde \Omega$, which reads
\begin{equation}
\pmb{ \xi} = \mathcal{X} \left( \mathbf{x}; \pmb{\mu} \right),
\label{eq_Transform}
\end{equation}
and thus the governing equations (\ref{eq_GoverningEqs}) are recast as follows:
\begin{equation}
\begin{aligned}
\mathcal{N}\left(\phi\left( \mathcal{X}^{-1} \left( \pmb{ \xi}; \pmb{\mu} \right) \right); \pmb{\mu}\right)
&:=\widetilde {\mathcal{N}} \left(\phi\left( \pmb{ \xi} \right); \pmb{\mu}\right)
=0,  \qquad \pmb{ \xi} \in \widetilde \Omega,
\\
\mathcal{B}\left(\phi\left(\mathcal{X}^{-1} \left( \pmb{ \xi}; \pmb{\mu} \right)\right); \pmb{\mu}\right)
&:=\widetilde {\mathcal{B}} \left(\phi\left( \pmb{ \xi} \right); \pmb{\mu}\right)
=0,  \qquad \pmb{ \xi} \in \partial \widetilde \Omega,
\end{aligned}
\label{eq_GoverningEqsForXi}
\end{equation}
where $\widetilde \Omega$ is the computational domain, $\widetilde {\mathcal{B}}$ and $\widetilde {\mathcal{N}}$ are the derived operators in computational space resulting from the transformation Eq. (\ref{eq_Transform}).

@@

Here we denote the discrete solutions of Eq ( \ref{eq_GoverningEqsForXi}) in vector form $\pmb{\phi} _h \in \mathbf{R}^{N  }$ and $\pmb{\phi} _h^{B} \in \mathbf{R}^{N_B}$ for parameter $\pmb{\mu}  \in \mathcal{P}$.
Given a suitable HF method, we have the governing Eq. (\ref{eq_GoverningEqsForXi}) in discrete form
\begin{align}
\mathbf{L}_{\widetilde {\mathcal{N}}}\pmb{\phi}_h +g_{\widetilde {\mathcal{N}}}(\pmb{\phi}_h, \pmb{\phi}_h^{B})
+\mathbf{C}_{\widetilde {\mathcal{N}}}
= 0,
\label{eq_DiscreteEqs}
\\
\mathbf{L}_{\widetilde {\mathcal{B}}} \pmb{\phi}_h + \mathbf{L}_{\widetilde {\mathcal{B}}}^{B} \pmb{\phi}_h^{B}
+\mathbf{C}_{\widetilde {\mathcal{B}}}
= 0,
\label{eq_DiscreteBoundary}
\end{align}
where $\mathbf{L}_{\widetilde {\mathcal{N}}} \in \mathbf{R}^{N \times N}$, $\mathbf{L}_{\widetilde {\mathcal{B}}} \in \mathbf{R}^{N_B \times N}$ and $\mathbf{L}_{\widetilde {\mathcal{B}}}^{B} \in \mathbf{R}^{N_B \times N_B}$ represent matrixes derived from linear parts of operators $\widetilde {\mathcal{N}}$ and $\widetilde {\mathcal{B}}$.
$\mathbf{C}_{\widetilde {\mathcal{N}}} \in \mathbf{R}^{N}$ and $\mathbf{C}_{\widetilde {\mathcal{B}}} \in \mathbf{R}^{N_B}$ are constant vectors independent of $\pmb{\phi} _h$ and $\pmb{\phi} _h^B$.
$g_{\widetilde {\mathcal{N}}}: \mathbf{R}^N \times \mathbf{R}^{N_B} \mapsto \mathbf{R}^N$ is a nonlinear function derived from the nonlinear part of operator $\widetilde {\mathcal{N}}$.

@@

\subsubsection{Chebyshev pseudospectral method}
In the Chebyshev pseudospectral method, the $d$-dimensional variable physical domain of  will be mapped into a unit regular computational domain $\widetilde \Omega =[-1,1]^d$,  each dimension discretized by  $N_p+1$ Chebyshev-Gauss-Lobatto points,
\begin{equation}
\xi_i=\cos \left( \frac{\pi i}{N_p} \right), \quad 0 \le i \le {N_p}.
\label{eq_CollocationPoints}
\end{equation}
Spatial derivatives in operators $\widetilde {\mathcal{N}}$ and $\widetilde {\mathcal{B}}$ are approximated with a matrix-vector multiplication in each dimension. In each dimension, the derivatives are approximated as follows:
\begin{equation}
\left. { \frac{\partial^s    \phi}{{\partial \xi^s}  }} \right|_{\xi _i }
 = \mathbf{D}^s \pmb{\phi},
\end{equation}
where $\pmb{\phi}=\{\phi _i\}_{i=0}^{N_p}$, $s$ is the order of derivative and $\mathbf{D}^s$ is the $s$th-order difference matrix of size ${(N_p+1)\times (N_p+1)}$ with entries defined by
\begin{equation}
D^0_{i,j} = \delta_{ij}, \qquad 0 \le i,j \le {N_p},
\label{eq_D0}
\end{equation}
\begin{equation}
\left\{ \begin{aligned}
&D_{i,j}^1 = \frac{{{B_i}}}{{{B_j}}}\frac{{{{( - 1)}^{i + n}}}}{{2\sin \left( {\frac{{(i + j)\pi }}{{2{N_x}}}} \right)\sin \left( {\frac{{(j - i)\pi }}{{2{N_p}}}} \right)}} \qquad 0 \le i,j \le {N_p},i \ne j\\
&D_{i,i}^1 =  - \sum\limits_{j = 0,j \ne i}^{{N_p}} {D_{i,j}^1} \quad 1 \le i \le {N_p} - 1\\
&D_{0,0}^1 =  - D_{{N_p},{N_p}}^1 =  - \frac{{2{N_p}^2 + 1}}{6}{\rm{                       }}\\
&{B_i} = \left\{
                 \begin{array}{*{20}{l}}
                      2 \qquad i=0, N_p \\
                      1 \qquad 1 \le i \le {N_p-1}
                 \end{array}
                 \right.
\end{aligned} \right. ,
\label{eq_D1}
\end{equation}
\begin{equation}
D^s_{i,j} = D^{1}_{i,k}D^{s-1}_{k,j} \qquad 0 \le i,j,k \le {N_p}.
\label{eq_Ds}
\end{equation}

For the following simulations of flow problems, the well known $IP_N-IP_{N-2}$ method \cite{zhang2010explicit} is adopted to prevent spurious pressure mode from
contaminating the flow fields \cite{peyret2013spectral}. In the $IP_N-IP_{N-2}$ method, pressure derivative is approximated without pressure values at boundary points, and thus pressure is approximated with polynomial of two order lower than all other field variables, such as velocity and temperature. All other variables are discretized with Eqs. (\ref{eq_D0})-(\ref{eq_Ds}) except that the first-order difference matrix $\mathbf{D}^{1}$ of pressure is replaced with $\hat {\mathbf{D}}^1$ as follows
\begin{equation}
\left\{ \begin{aligned}
&\hat D_{i,j}^1 = 0                              & i=0,N_p \text{  or } j=0, N_p \\
&\hat D_{i,i}^1 = \frac{3\xi_i}{2(1-\xi_i^{2})}  & 1 \le i \le N_p-1\\
&\hat D_{i,j}^1 = \frac{(-1)^{i+j}(1-\xi_j^{2})}
{2(1-\xi_i^{2})(\xi_i-\xi_j)} \qquad             & 1 \le i \ne j \le N_p-1\\
\end{aligned} \right. .
\label{eq_D1}
\end{equation}

@@

\subsection{Reduced-order model}
\label{sec_ROM}
As for solving the problem in Eq. (\ref{eq_GoverningEqsForXi}), full-order model is always suffering from large computational cost since the required degrees of freedom $N$ is always very large.  Therefore, we are interested in replacing the full-order model with a well-posed  reduced-order model to represent main dynamic of the system. The full-order model is termed as reducible when high-fidelity solution $\pmb{\phi} _h$ can be well approximated in $m$-dimensional subspace $\mathcal{V}=\mathbf{R}^{N \times m}$. The subspace is spanned by a suitable set of basis vectors $\{\mathbf{V}_i \in \mathbf{R}^{N} \}_{i=1}^m$.  Note that the the size of problem will be largely reduced, only if $m \ll N$. The full-order solution of the interior DOFs $\pmb{\phi} _h$ can be projected into the subspace $\mathcal{V}$ by
\begin{equation}
\begin{aligned}
\pmb{\phi} _h  &   =   \mathbf{V} \pmb{\alpha} + \tilde{\phi} + \pmb{\epsilon}
               &\approx \mathbf{V} \pmb{\alpha} + \tilde{\phi},
\end{aligned}
\label{eq_projection}
\end{equation}
where $\mathbf{V} \in \mathbf{R}^{N\times m}$ is a matrix with the basis vectors as its columns, $\pmb{\alpha}$ is   the projection coefficients, $\pmb{\epsilon}$ is the projection error. $\tilde{\phi} \in \mathbf{R}$ is independent of $\pmb{\mu}$, intended for filtering a constant value to avoid its domination on the basis, and usually it can be set as the average. The boundary conditions in Eq. (\ref{eq_DiscreteBoundary}) say that the interior DOFs have a linear relationship with interior DOFs. Thus, we can enforce the boundary conditions without any reduction. The procedure keeps the reduced-order model of high accuracy at bounaries and avoid shifting of boundary values. According to Eq.(\ref{eq_DiscreteBoundary}), the boundary DOFs can be denoted as follows
\begin{equation}
\pmb{\phi}_h^{B} = -( \mathbf{L}_{\widetilde {\mathcal{B}}}^{B} )^{-1}
\left(
\mathbf{L}_{\widetilde {\mathcal{B}}} \pmb{\phi}_h +
\mathbf{C}_{\widetilde {\mathcal{B}}}
\right).
\label{eq_DerivePhiB}
\end{equation}

Substituting Eq. (\ref{eq_projection}) and (\ref{eq_DerivePhiB}) into Eq. (\ref{eq_DiscreteEqs}), we have the overdetermined system for interior
DOFs
\begin{equation}
\mathbf{L}_{\widetilde {\mathcal{N}}} \mathbf{V} \pmb{\alpha}
+\mathbf{g}_{\widetilde {\mathcal{N}}}
\left( \mathbf{V} \pmb{\alpha} + \tilde{\phi} + \pmb{\epsilon}, -\left( \mathbf{L}_{\widetilde {\mathcal{B}}}^{B} \right)^{-1}
\left(
\mathbf{L}_{\widetilde {\mathcal{B}}} \mathbf{V} \pmb{\alpha} +
\mathbf{C}_{\widetilde {\mathcal{B}}} + \mathbf{L}_{\widetilde {\mathcal{B}}} \mathbf{I} \tilde{\phi} + \mathbf{L}_{\widetilde {\mathcal{B}}} \pmb{\epsilon}
\right) \right)
+\mathbf{L}_{\widetilde {\mathcal{N}}} \mathbf{I} \tilde{\phi}
+\mathbf{L}_{\widetilde {\mathcal{N}}} \pmb{\epsilon}
+ \mathbf{C}_{\widetilde {\mathcal{N}}}
= 0,
\label{eq_Overdetermined0}
\end{equation}
where $\mathbf{I} \in \mathbf{R}^{N}$ is an vector filled with 1. For the sake of clarity, Eq. (\ref{eq_Overdetermined0}) can be rearranged in the simplified form
\begin{equation}
 \mathbf{L} \mathbf{V} \pmb{\alpha}
+ g         \left( \mathbf{V} \pmb{\alpha} \right)
+\mathbf{C}
= \tilde{ \pmb{\epsilon} },
\label{eq_Overdetermined1}
\end{equation}
where $\mathbf{L} \in \mathbf{R}^{N \times N}$, $\mathbf{C} \in \mathbf{R}^{N}$ and $g: \mathbf{R}^N \mapsto \mathbf{R}^N$ are a matrix, vector and function derived from Eq. (\ref{eq_Overdetermined0}), respectively.
The quantity $\tilde{ \pmb{\epsilon} }$ represent the residual resulting from the projection error $\pmb{\epsilon}$.
In the framework of Petrov-Galerkin projection, if we consider a basis $\mathbf{W} \in \mathbf{R}^{N \times m}$ that is orthogonal to the residual,  the overdetermined system is reduced to a system of $m$ equations
\begin{equation}
\mathbf{W}^T
\left(
 \mathbf{L} \mathbf{V} \pmb{\alpha}
+\mathbf{g} \left( \mathbf{V} \pmb{\alpha} \right)
+\mathbf{C}
\right)
=0.
\label{eq_Petrov}
\end{equation}
In this work, we employ the Galerkin framework, namely $\mathbf{W}$=$\mathbf{V}$.
Thus, we have the reduced-order model as follows:
\begin{equation}
\mathbf{V}^T
\left(
 \mathbf{L} \mathbf{V} \pmb{\alpha}
+ g         \left( \mathbf{V} \pmb{\alpha} \right)
+\mathbf{C}
\right)
=0.
\label{eq_Galerkin}
\end{equation}
